Title

### 2023-06-23 main.tex
Citas

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}. 
% Several 
% kinds of quantum systems have been simulated, like \cpnote{PONER ALGO ACA Y CITAR. 
% Te puedes inspirar en las introducciones de articulos que simulen sistemas cuanticos}. 
Being open quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts
towards the simulation of the evolution of open quantum
systems~\cite{cleve,Zanetti,Xin,Wei}.\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.} \tbnote{La primera habla al principio en general
de simulación de sistemas abiertos y los otros tres porque se relacionan más con este trabajo
porque lo hacen en particular con el formalismo de canales cuánticos}
Such systems have been simulated because of their many applications, 
such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
studying dissipative processes~\cite{Barreiro}
and modeling non-Markovian dynamics~\cite{Marsden}.
Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
and withing them, the simplest class of channels that produce decoherence are
Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.

@@

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for the particular case of single-qubit Pauli channels. 
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem,
which  sets the mathematical conditions for the transformations
that can be done using a parametrized circuit with the condition that only a
controlled \cpnote{el caso general es controlado, correcto?} \tbnote{Sí} single-qubit
operation in the circuit may depend on the parameter.  Finally, in
section \ref{sec: 1PR circuit for a Pauli map}, we conclude about the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

>>>>

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}. 
% Several 
% kinds of quantum systems have been simulated, like \cpnote{PONER ALGO ACA Y CITAR. 
% Te puedes inspirar en las introducciones de articulos que simulen sistemas cuanticos}. 
Being open quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts
towards the simulation of the evolution of open quantum
systems~\cite{cleve,Zanetti,Xin,Wei}.\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.}
\tbnote{Cambié un poco, agregué unos artículos que vi mucho más populares:}
{\color{purple} 
open quantum systems~\cite{Garcia, Wang,Weimer} and specifically for
quantum channels~\cite{Xin,Wei,Zanetti}.
}

Such systems have been simulated because of their many applications, 
such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
studying dissipative processes~\cite{Barreiro}
and modeling non-Markovian dynamics~\cite{Marsden}.
Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
and withing them, the simplest class of channels that produce decoherence are
Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.

@@

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for the particular case of single-qubit Pauli channels. 
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem,
which  sets the mathematical conditions for the transformations
that can be done using a parametrized circuit with the condition that only a
controlled single-qubit
operation in the circuit may depend on the parameter.  Finally, in
section \ref{sec: 1PR circuit for a Pauli map}, we conclude about the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.
